---
title: "p8105_hw5_jz3036"
output: github_document
author: "Junyuan Zheng (jz3036)"
date: 2018-11-04
---

* Import necessary packages.
```{r import_packages}
library(tidyverse)
#library(readxl)
```

# Problem 1

* Start with a dataframe containing all file names.
```{r file_names}
file_names = list.files(path = './data') %>%
  tibble('subject' = .)
head(file_names) %>% 
  knitr::kable() 
```

* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe.
```{r read_in_tables, message = FALSE}
data = 
  file_names %>% 
  mutate(., path = paste('./data/', subject, sep='')) %>% 
  mutate(., arm_data = map(.x = path, ~read_csv(file = .x)))
head(data) %>% 
  knitr::kable() 
```

* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary.
```{r tidy_data}
tidy_data = 
  select(data, subject, arm_data) %>% 
  unnest(.,) %>%
  mutate(., subject = str_replace(subject, '.csv', '')) %>% 
  separate(., subject, into = c('group','subject_id'), sep = '_') %>% 
  gather(., key = week, value = observation, week_1:week_8) %>% 
  mutate(., week = str_replace(week, 'week_', ''))
head(tidy_data) %>% 
  knitr::kable() 
```

* Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r spaghetti_plot}
tidy_data %>% 
  ggplot(., aes(x = week, y = observation, group=interaction(group, subject_id), color = subject_id, shape = group)) +
  geom_point(color = 'black', size = 3, alpha = 0.8, stroke = 1) +
  scale_shape_manual(values=c(1,2)) +
  geom_line() +
  labs(title = 'Spaghetti Plot for Each Subject') +
  theme(plot.title = element_text(hjust = 0.5))
```
As shown by the spaghetti plot above, the experimental group (triangle) is generally higher than the control group (circle) on observation across these 8 weeks.

# Problem 2

```{r data_import_p2}
data_p2 = 
  read_csv(file='./homicide_data/homicide-data.csv')
```

* Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

This is a dataset collected by Washington Post regarding criminal homicide over the past years in 50 America cities.The raw data contains `r nrow(data_p2)` rows/observations, and `r ncol(data_p2)` columns/variables. Variables mainly includes the victims' personal info such as name, race and sex, as well as the location info of the cases, including city, state and coordinates.

```{r by_city}
data_p2 %>%  
  mutate(., city_state = paste(city, state, sep = ', ')) %>% 
  group_by(., city_state) %>% 
  summarize(., case_number = n(),
               case_unsolved = 
               sum(disposition == 'Closed without arrest' | disposition == 'Open/No arrest'))
```

