---
title: "p8105_hw5_jz3036"
output: github_document
author: "Junyuan Zheng (jz3036)"
date: 2018-11-04
---

* Import necessary packages.
```{r import_packages}
library(tidyverse)
#library(readxl)
```

# Problem 1

* Start with a dataframe containing all file names.
```{r file_names}
file_names = list.files(path = './data') %>%
  tibble('subject' = .)

```

* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe.

```{r read_in_tables, message = FALSE}
data = 
  file_names %>% 
  mutate(., path = paste('./data/', subject, sep='')) %>% 
  mutate(., arm_data = map(.x = path, ~read_csv(file = .x)))
```

* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r tidy_data}
tidy_data = 
  select(data, subject, arm_data) %>% 
  unnest(.,) %>%
  mutate(., subject = str_replace(subject, '.csv', '')) %>% 
  separate(., subject, into = c('group','subject_id'), sep = '_') %>% 
  gather(., key = week, value = observation, week_1:week_8) %>% 
  mutate(., week = str_replace(week, 'week_', ''))
```

